Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-02 outputs/paper/paper.Rmd
ggplot

# Data
```{r, include=FALSE, echo=FALSE}
# Read the extracted and cleaned data, data extraction done in 01-gather-data.R and modification done in 02-clean-and-prepare-data.R
data <- read_csv("outputs/data/cleaned_data.csv")
```

```{r}
data %>%
  ggplot(aes(x = Variable, y = Health_Record)) +
  geom_bar(stat='identity') +
  coord_flip()
```

Talk more about it.

@@

```{r}

```

>>>>

# Data
```{r, include=FALSE, echo=FALSE}
# Read the extracted and cleaned data, data extraction done in 01-gather-data.R and modification done in 02-clean-and-prepare-data.R
data <- read_csv("outputs/data/cleaned_data.csv")

urban_rural <- pivot_longer(data[1:2, 1:5], -Variable, names_to="immune_status", values_to="value")
region <- pivot_longer(data[3:7, 1:5], -Variable, names_to="immune_status", values_to="value")
education <- pivot_longer(data[8:11, 1:5], -Variable, names_to="immune_status", values_to="value")
religion <- pivot_longer(data[12:13, 1:5], -Variable, names_to="immune_status", values_to="value")
total <- pivot_longer(data[14, 1:5], -Variable, names_to="immune_status", values_to="value")
population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)

# create new dataset only for urban-rural data
# urban_rural <- data.frame(location = c(rep("urban", data[1,6]), rep("rural", data[2,6])),
#                 immune_data =  c(rep("Health Report", round(data[1,2]*data[1,6]/100)), rep("Mothers Report", round(data[1,3]*data[1,6]/100)), rep("No immune", round(data[1,5]*data[1,6]/100)), 
#                                  rep("Health Report", round(data[2,2]*data[2,6]/100)), rep("Mothers Report", round(data[2,3]*data[2,6]/100)), rep("No immune", round(data[2,5]*data[2,6]/100)))
#                 
#                 )

# create new dataset only for for region
# region <- data.frame(region = c(rep("north", data[3,6]), rep("north_east", data[4,6]), rep("central", data[5,6]), rep("south", data[6,6]), rep("bangkok", data[7,6])),
#                     immune_data =  c(rep("Health Report", round(data[3,2]*data[3,6]/100)), rep("Mothers Report", round(data[3,3]*data[3,6]/100)), rep("No immune", round(data[3,5]*data[3,6]/100)), 
#                                  rep("Health Report", round(data[4,2]*data[4,6]/100)), rep("Mothers Report", round(data[4,3]*data[4,6]/100)), rep("No immune", round(data[4,5]*data[4,6]/100)),
#                                  rep("Health Report", round(data[5,2]*data[5,6]/100)), rep("Mothers Report", round(data[5,3]*data[5,6]/100)), rep("No immune", round(data[5,5]*data[5,6]/100)), 
#                                  rep("Health Report", round(data[6,2]*data[6,6]/100)), rep("Mothers Report", round(data[6,3]*data[6,6]/100)), rep("No immune", round(data[6,5]*data[6,6]/100)),
#                                  rep("Health Report", round(data[7,2]*data[7,6]/100)), rep("Mothers Report", round(data[7,3]*data[7,6]/100)), rep("No immune", round(data[7,5]*data[7,6]/100)))
#                     )

# create new dataset only for for education. due to an error in the dataset provided by DHS, some rows will be filled with NA.

 # no_edu <-data.frame(education = c(rep("no_edu", 265)),
 #                     immune_data = c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)))
 #                     )
 # 
 # primary <-data.frame(education = c(rep("primary", data[9,6])),
 #                     immune_data = c(rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", floor(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)))
 #                     )
 # 
 # secondary <-data.frame(education = c(rep("secondary", data[10,6])),
 #                     immune_data = c(rep("Health Report", floor(data[10,2]*data[10,6]/100)), rep("Mothers Report", floor(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)))
 #                    )
# education <- data.frame(education = c(rep("no_education", round(data[8,2]*data[8,6]/100) + round(data[8,3]*data[8,6]/100) + round(data[8,5]*data[8,6]/100)), 
#                                       rep("primary", round(data[9,2]*data[9,6]/100) + round(data[9,3]*data[9,6]/100) + round(data[9,5]*data[9,6]/100)), 
#                                       rep("secondary", round(data[10,2]*data[10,6]/100) + round(data[10,3]*data[10,6]/100) + round(data[10,5]*data[10,6]/100)),
#                                       rep("higher", round(data[11,2]*data[11,6]/100) + round(data[11,3]*data[11,6]/100) + round(data[11,5]*data[11,6]/100))),
#                     immune_data =  c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)),
#                                  rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", round(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)),
#                                  rep("Health Report", round(data[10,2]*data[10,6]/100)), rep("Mothers Report", round(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)),
#                                  rep("Health Report", round(data[11,2]*data[11,6]/100)), rep("Mothers Report", round(data[11,3]*data[11,6]/100)), rep("No immune", round(data[11,5]*data[11,6]/100)))
#                     )

# create new dataset only for for education
# religion <- data.frame(religion = c(rep("Buddhist", data[12,6]), rep("Islam", data[13,6])),
#                 immune_data =  c(rep("Health Report", round(data[12,2]*data[12,6]/100)), rep("Mothers Report", round(data[12,3]*data[12,6]/100)), rep("No immune", round(data[12,5]*data[12,6]/100)), 
#                                  rep("Health Report", round(data[13,2]*data[13,6]/100)), rep("Mothers Report", round(data[13,3]*data[13,6]/100)), rep("No immune", round(data[13,5]*data[13,6]/100)))
#                       )
# 
# total <- data.frame(total = c(rep("total", data[14,6])),
#                 immune_data =  c(rep("Health Report", floor(data[14,2]*data[14,6]/100)), rep("Mothers Report", floor(data[14,3]*data[14,6]/100)), rep("No immune", floor(data[14,5]*data[14,6]/100)))
#                       )
```

```{r}
population %>%
  ggplot(aes(x = Variable, y = Population, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
Talk more about it.

@@

```{r}
total %>%
  ggplot(aes(x = immune_status, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
